\name{}: Supplement data

### 2021-07-13 paper/supplement/supplement.tex
.
Update heatmap and distribution figures and their caption in supplement

\clearpage
\begin{figure}[ht]%figure1
	\centerline{\includegraphics[width=1.1\textwidth]{../figures/ATC_Interpro_heatmap.png}}
	\caption{Heatmap showing the results of the ATC drug class and InterPro family prediction analysis}
	\label{fig:ATCInterproHeatmap}
\end{figure}

@@

>>>>

@@

\clearpage
\begin{figure}[ht]%figure1
	\centerline{\includegraphics[width=1.1\textwidth]{../figures/ATC_Interpro_heatmap.png}}
	\caption{Heatmap showing the results of the ATC drug class and InterPro family prediction analysis. The figure shows the proportion of false negatives compared to the total amount of drugs in the corresponding level 2 ATC class. While few ATC classes show a high share of novel interactors, this is mainly due to the total amount of drugs in the ATC class. For more information note the correspondence with Supplementary Figure 6.}
	\label{fig:ATCInterproHeatmap}
\end{figure}

\begin{figure}[ht]%figure1
	\centerline{\includegraphics[width=1\textwidth]{../figures/ATC_bar_distr.png}}
	\caption{Amount of drugs used in the ATC/InterPro analysis for each level 2 ATC class. Notably, some of the classes have only few or single drug members.}
	\label{fig:ATCdistribution}
\end{figure}
